\LARGE \bf When Children Teach a Robot to Write

### 2014-12-10 main.tex
Rewrite paragraph on mistake classification

%todo
In~\cite{Chandra2013}, it was found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes classified
as inappropriate \emph{internal proportions} or \emph{global deformations}. It
would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
the same general categories.

Using a database of children's letters when
available may yield potential for parameterising other mistakes made by
children, such as merging strokes or decomposing a shape into multiple subparts
inappropriately. Nevertheless, our current shape model
generated from PCA on a dataset of only adults' writing has shown to be
initial well-suited to generate `poor' letters which are appropriate for 
simulating a na\"ive learner.

>>>>

In~\cite{Chandra2013}, Chandra found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes
qualitatively classified as inappropriate \emph{internal proportions} or
\emph{global deformations}. As exemplified in Figure \ref{fig:sampleLetters},
the shapes generated by the system exhibit the same kind of deformities. Chandra
identifies other, less common, mistakes that involve topological changes (like
letters being broken in subparts, extra strokes, etc.). Using a database of
children's letters when available may yield potential for better parameterizing
these other mistakes. However, as an initial approximation, the shape models
generated from PCA on a dataset of only adults' writing have shown to be
well-suited to generate `poor' letters that children were able to recognize and
successfully improve.
